Due to the fact that our SFs are defined as a double ratio, we expect some of the systematic uncertainties to cancel at least at first order. Therefore, luminosity, light-lepton and physics modelling uncertainties are expected to be reduced. Unfortunately, tau calibration and MJ background estimation uncertainties do not cancel in the double ratio method. Then, we expect them to dominate the measurement precision.

After calculating the integrated luminosity uncertainty for the SFs, we find that it is less than $0.07\%$, so we just ignore it in our final results. For our uncertainties calculation we use the standard ATLAS procedure. In this method, the objects are re-calibrated using parameters one sigma away from the central value. The results are then compared between the nominal and the re-calibrated events and the difference is quoted as the uncertainty. 

In this chapter the systematic uncertainties are presented for the $Z\to\tauhad\mu$ final state. Appendix . contains the results for $Z\to\tauhade$, overall the conclusions are the same for both. The systematic uncertainties used to report the SFs are presented in Table \ref{Tab5}. 
\begin{table}[htbp]
	\centering
	\begin{tabular}{cc}
		\hline
		\multicolumn{1}{|c|}{Source}        & \multicolumn{1}{c|}{Sys. Uncertainty (\%)} \\ \hline
		Electron ID efficiency              & 0.8                                        \\
		Muon ID Efficiency                  & 0.2                                        \\
		Electron $\pt$ scale and resolution & 0.4                                        \\
		Muon $\pt$ scale and resolution     & 0.3                                        \\
		Tau $\pt$ scale                     & 1.9                                        \\
		Electron trigger efficiency         & 0.1                                        \\
		Muon trigger efficiency             & 0.4                                        \\ 
	\end{tabular}
	\caption{Systematic uncertainties used in this study. At the time of writing this report we have not directly estimated all of our systematic uncertainties. However, we expect that some of them will get reduced by the double ratio method.}
	\label{Tab5}
\end{table}

